---
title: 'Gypsy: zonal-based gypsum application recommendation'
# author: "Chloe Lai"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## `r input$fieldName_z`

### `r paste0('Crop: ', input$cropType)`

Projected additional income (\$) p.a. for the field is `r round(zRate()$incAdd, digits = 2)`.

Estimated total cost of gypsum application (\$) based on recommendation for the field is `r round(zRate()$cost, digits = 2)`. 

Projected net benefit (\$) over time period for the field is `r round(zRate()$netBen, digits = 2)`. 

Total gypsum (t) required to completely ameliorate ESP to the desired ESP for the field is `r round(sum(zRate()$dfb$gR), digits = 2)`. 

```{r table1, echo=FALSE}

kable(zRate()$dfa, escape = F, col.names = c('Zone Name', 'Zone Area (ha)',
                                             'Recommended Gypsum Application Rate (t/ha)',
                                             'Total Gypsum Recommended to Apply (t)',
                                             'Projected Yield Increase (t)',
                                             'Predicted Additional Income (&#36;)'))%>% #replace column name with sensible display
  column_spec(1, bold = T) %>%
  kable_styling(
    font_size = 15,
    bootstrap_options = c("striped", "hover", "condensed","responsive")
  )

    
```



```{r table2, echo=FALSE}

df <- zRate()$dfb[c('ZoneName','gR','ESP', 'ESPf')] 
row.names(df) <- NULL
df[,2:4] <- round(df[,2:4], digits = 2)
kable(df, escape = F, col.names = c('Zone Name', 
                                    'Estimated Gypsum Requirement for Each Depth for the Zone Area(t)',
                                    'Initial ESP for Each depth',
                                    'Final ESP based on Maximizing Net Benefit')) %>%
  column_spec(1, bold = T) %>%
  kable_styling(
    font_size = 15,
    bootstrap_options = c("striped", "hover", "condensed","responsive"))

```


